---
title: "analysis"
output: html_document
date: '2022-04-25'
---

# Setup

```{r setup}
library(tidyverse)
library(here)
library(targets)
library(plotly)

knitr::opts_knit$set(root.dir = here::here())

```

# Targets list

```{r}


tar_manifest()
tar_manifest() %>% View
```







# Pipeline
## Whole Pipeline
```{r}
tar_visnetwork(level_separation = 600)
tar_visnetwork(level_separation = 600, targets_only = TRUE)



```

## Data Preparation
```{r}
tar_visnetwork(names = contains("wrang") | contains("merged"), level_separation = 400)











```

## Feature Extraction
```{r}
tar_visnetwork(names = contains("model_input"), level_separation = 400)



```




## Model Fit
```{r}
tar_visnetwork(names = contains("jags") & !contains("lastweek"), level_separation = 400)
```

## Model Fit Check
```{r}
tar_visnetwork(names = contains("post"), level_separation = 400)
```


## Model Predictive Power 
```{r}
tar_visnetwork(
    names = contains("waic") | contains("loo"), 
    level_separation = 400
)

```



## Model Forecast
```{r}
tar_visnetwork(names = contains("forecast"), level_separation = 600)
```







## Export results
```{r}

tar_visnetwork(names = contains("export"), level_separation = 400)

```


# Best Model
```{r}
tar_read(loo_model_comparison_2017)
tar_read(loo_model_comparison_2017) %>% View



```



 


# Summary of best model 

```{r}
tar_read(jags_2017_summary_model_M1_b0_N)
tar_read(jags_2017_summary_model_M1_b0_N) %>% View


```


# Posterior check of best model 

```{r}

tar_read(post_check_M1_b0_N_2017)


tar_read(post_check_M1_b0_N_2017) %>% map(ggplotly)
```


# Forecast of best model 
```{r}

# Forecast computed data
tar_manifest(contains("forecast"))
tar_read(lastweek_forecast_jagsfit_M1_b0_2017)


# Forecast plots
## Abundance plots
tar_read(plots_lastweek_forecast_M1_b0_2017)$plots$abundance
tar_read(plots_lastweek_forecast_M1_b0_2017)$plots$abundance %>% map(ggplotly)
## Density plots
tar_read(plots_lastweek_forecast_M1_b0_2017)$plots$density
tar_read(plots_lastweek_forecast_M1_b0_2017)$plots$density %>% map(ggplotly)





```





# Forecast model loo_model_comparison_2017
```{r}
## Density
tar_read(plots_lastweek_forecast_allmodels_2017)[[1]]
tar_read(plots_lastweek_forecast_allmodels_2017)[[1]] %>% map(ggplotly)

## Abundance
tar_read(plots_lastweek_forecast_allmodels_2017)[[2]]
tar_read(plots_lastweek_forecast_allmodels_2017)[[2]] %>% map(ggplotly)



```



# Model weights
```{r}
tar_read(loo_model_weights_2017)
tar_read(loo_model_weights_2017) %>% View
```






# Uncertainty analysis
```{r}
# Lineplot
tar_read(uncertainty_analysis_2017)$lineplot
tar_read(uncertainty_analysis_2017)$lineplot %>% ggplotly

tar_read(uncertainty_analysis_2017)$ridgeplot

tar_read(uncertainty_analysis_2017)$uncertainty
tar_read(uncertainty_analysis_2017)$uncertainty %>% ggplotly


```




```{r}
tar_read("wrangled_ecmwf_data_2017")

tar_manifest(contains("wrangled"))$name


```

Models

```{r}
tar_manifest(contains("file_model"))$name

```


JAGS summary of each model
```{r}

tar_manifest(contains("summary"))


tar_read(jags_2017_summary_model_M2_b0) %>% View




```















Posterior checks
```{r}

tar_manifest(contains("post"))
```




















